---
title: "Tuberculosis Incidence: England and Wales, 1913-2016"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    storyboard: true
    runtime: shiny
    theme: cosmo
    social: menu
    source: "https://github.com/seabbs/TB_England_Wales"
    navbar:
      - { title: "By Sam Abbott", href: "https://samabbott.co.uk", align: right }
    css: style.css
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(plotly)
library(DT)
library(tidyverse)
library(tbinenglanddataclean)
```
    
```{r global, include = FALSE}
## Set up interventions table
df_interventions <- tbinenglanddataclean::tb_interventions_timeline %>% 
    rename(Year = year, 
           Intervention = intervention,
           Type = type,
           Line = line,
           Detail = detail)
```

### Tuberculosis notifications in England and Wales from 2013 to 2016, stratified initially by respiratory/non-respiratory status and from 1982 by pulmonary/non-pulmonary Tuberculosis. Interventions are highlighted with vertical lines, more information on each intervention is available in the following table. The data is sourced from Public Health England, see [here](https://www.gov.uk/government/publications/tuberculosis-tb-annual-notifications-1913-onwards) for details.

```{r}
renderPlotly({
  plot <- tbinenglanddataclean::plot_historic_tb_ew(zoom_date_start = NULL) 
  plot <- plotly_build(plot)
  plot$elementId <- NULL

  plot
})
```

### Interventions against Tuberculosis, aggregated from multiple sources but based in part on this [wikipedia timeline](https://en.wikipedia.org/wiki/Timeline_of_tuberculosis).

```{r}
DT::renderDataTable({
  df_interventions}, options = list(
  pageLength = 20,
  scrollY = "600px", scrollX = TRUE,
  fillContainer = TRUE,
  filter = "top"
)
)
```

### Proportion of Tuberculosis by type. From 1913 until 1981 the plot shows the proportion of respiratory vs. non-respiratory cases. From 1982 it shows the proportion of pulmonary vs. non-pulmonary Tuberculosis.

```{r}
renderPlotly({
  plot <- tbinenglanddataclean::plot_historic_prop_pul_tb() +
  labs(caption = "Source: Public Health England")
  plot <- plotly_build(plot)
  plot$elementId <- NULL
  plot
})
```